Delone lattice studies in \CIII, the space of three complex variables

### 2023-07-14 C3/C3.tex
uv5017,uv5018,uv5019 fixing reviewer comments and page proofs

	\begin{table}	
		\label{tab:operators}
		\caption{The Result column values give the products of each operator as applied to $(x_j, y_j)$}.
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\mathcal{P}_r$ 	& $ \mathcal{P}_r(c_j)$ 	& $(x_j, x_j)$ 		& Plus real\\ 
			$\mathcal{P}_i$ 	&  $\mathcal{P}_i(c_j)$  	& $(y_j, y_j)$ 		& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ or $(x_j,0)$		& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ pr $(y_j,0)$ 		& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

Element 1 of result vector is (-\si,~\siv-\si ), and
it is created by multiplying the beginning \CIII{} vector by the
first row of the transformation matrix. In this case, we see
that \ci of the result only contains scalars from \ci of
the input, so the first row must contain some operator to
be multiplied times input \ci, and the second and third
elements of the matrix row must be zero. We create an operator
($Minus~real$) to transform the input \ci to the output \ci; so
the first row of the reduction matrix is: $\Minus{}_i	 0		 0$.

Element 2 of the result vector is (\siii+\si,~\sii+\si),
and
it is created by multiplying the beginning \CIII{} vector by the
second row of the transformation matrix. The result \cii
contains \si in both the real and imaginary parts. So
the first matrix element in that row must insert \si, the
real part of the input \ci, into both the real and imaginary
parts. An operator to produce that is created 
(Plus{}~real). Next we see that the result contains \sii and \siii.
\siii appears in the real part of the result element and in the
third part of the input vector. So the third element of the 
second matrix row must extract the \siii, the real part of 
\ciii of the input. So the second row now contains the Plus real
operator and the element to put the  real part of \ciii of the input.
The final matrix element of the second row (the second element)
must extract the real part of input \cii and place it in the
imaginary part of the output vector. The resulting second
row of the matrix is $\Plus_r~\Real~i\Real$.

Using similar logic, the third row of the matrix is:
$\Plus_r~\Imaginary~i\Imaginary$.

>>>>

	\begin{table}	
		\label{tab:operators}
		\caption{The Result column values give the products of each operator as applied to $(x_j, y_j)$}.
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\mathcal{P}_r$ 	& $ \mathcal{P}_r(c_j)$ 	& $(x_j, x_j)$ 		& Plus real\\ 
			$\mathcal{P}_i$ 	&  $\mathcal{P}_i(c_j)$  	& $(y_j, y_j)$ 		& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ or $(x_j,0)$		& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ or $(y_j,0)$ 		& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

Element 1 of result vector is (-\si,~\siv-\si ), and
it is created by multiplying the beginning \CIII{} vector by the
first row of the transformation matrix. In this case, we see
that \ci of the result only contains scalars from \ci of
the input, so the first row must contain some operator to
be multiplied times input \ci, and the second and third
elements of the matrix row must be zero. We create an operator
($Minus~real$) to transform the input \ci to the output \ci; so
the first row of the reduction matrix is: $\Minus{}_r	 0		 0$.

Element 2 of the result vector is (\siii+\si,~\sii+\si),
and
it is created by multiplying the beginning \CIII{} vector by the
second row of the transformation matrix. The result \cii
contains \si in both the real and imaginary parts. So
the first matrix element in that row must insert \si, the
real part of the input \ci, into both the real and imaginary
parts. An operator to produce that is created 
(Plus{}~real). Next we see that the result contains \sii and \siii.
\siii appears in the real part of the result element and in the
third part of the input vector. So the third element of the 
second matrix row must extract the \siii, the real part of 
\ciii of the input. So the second row now contains the Plus real
operator and the element to put the  real part of \ciii of the input.
The final matrix element of the second row (the second element)
must extract the real part of input \cii and place it in the
imaginary part of the output vector. The resulting second
row of the matrix is $\Plus_r~i\Real~\Real$.

Using similar logic, the third row of the matrix is:
$\Plus_r~i\Imaginary~\Imaginary$.
